Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-09 article/article.Rmd
Commit 2024-06-09 21:11

```

@@

<!-- Aerosol change -->
The above clear sky reference values are based on the climatological AOD and WC,
hence they cannot describe accurately the long term variation of
$\text{GHI}_\text{ref}$ due to changes in the two atmospheric constituents, mainly
AOD.  As reported by @Natsis2023, there is a long term brightening effect in the GHI
data of Thessaloniki for the period 1993 -- 2023, which for clear-sky data was
attributed to long-term changes in aerosol effects.

In order to better incorporate this change, we used, estimations of AOD change
derived from two sources. For 1993 -- 2005, @Kazadzis2007 have found a change of
$-3.8\,\%$ per year at AOD on $340\,\text{nm}$, using a Brewer spectrophotometer. For
2005 to 2023, we derived the trend from the available monthly climatological data of AERONET.

@@

According to @Kazadzis2007, in the period 1997 -- 2005, the mean AOD of
$340\,\text{nm}$ was calculated to $0.403$ with the use of a Brewer
spectrophotometer, with a linear trend of $-3.8±0.93\,\%$ per year.  This corresponds
to a change of $0.0153$ per year for the AOD of $340\,\text{nm}$ .  Using the alpha Ångström
coefficient of $\alpha = 1.6$, this translates to a change in Ångström beta
coefficient of $\beta=0.00272$ per year (or $\beta=0.084$ in 1997 and $\beta=0.059$
in 2005).  By interpolating the resulting clear sky irradiance, we have a trend of
$+0.21\,\%$ per year for the clear sky irradiance.  For the period 2005 -- 2005 we
used the mean monthly values from AERONET, with a similar simulation scheme. We
computed the trend of clear sky radiation for each month of the year, which gave us a
mean clear sky radiation trend of $+0.14\,\%$ per year. We applied this long term
change to the clear sky irradiance, in order to create a more realistic
representation of the irradiance for the whole study period
(Figure\nobreakspace{}\ref{fig:CS-change}).

>>>>

BR <- readRDS("~/MANUSCRIPTS/02_enhancement/data/Model_CS_trend.Rds")
BR <-  unique(BR[typer == "BR SZA 55", .(year, pw_avg_mm, b, a)])
```

@@

<!-- Aerosol change -->
The above clear sky reference values are based on the climatological AOD and WC,
hence they cannot describe accurately the long term variation of
$\text{GHI}_\text{ref}$ due to changes in the two atmospheric constituents, mainly
AOD.  As reported by @Natsis2023, there is a long term brightening effect in the GHI
data of Thessaloniki for the period 1993 -- 2023, which for clear-sky data was
attributed to long-term changes in aerosol effects.  Therefore, an adjustment of the
$\text{GHI}_\text{ref}$ used in this study is necessary. As AERONET data start only
in 2003, we used for the period 1993 -– 2005 estimates of changes in AOD at
$340\,\text{nm}$ derived from a collocated Brewer spectrophotometer derived from two
sources. For 1993 -- 2005 [@Kazadzis2007] to calculate the trend in
$\text{GHI}_\text{ref}$ during this period.

<!--
$-3.8\,\%$ per year at AOD on $340\,\text{nm}$, using a Brewer spectrophotometer. For
-->

@@

According to this study, in the period 1997 -- 2005, the mean AOD at $340\,\text{nm}$
$0.403$ with a trend of $-3.8±0.93\,\%$ per year, corresponding to a change of
$0.0153$ per year.  Using an Ångström coefficient $\alpha = 1.6$, this translates to
a change in the Ångström coefficient $\beta=0.00272$ per year (or $\beta=0.084$ in
1997 and $\beta=0.059$
in 2005).

Simulations with uvspec for the above Ångström coefficients, with WC of $`r
round(BR[year==1997, pw_avg_mm],1)`\,\text{mm}$ and $`r round(BR[year==2005,
pw_avg_mm],1)`\,\text{mm}$ for 1997 and 2005 respectively and for a SZA of $55^\circ$

By interpolating the resulting clear sky irradiance, we have a trend of
$+0.21\,\%$ per year for the clear sky irradiance.  For the period 2005 -- 2005 we
used the mean monthly values from AERONET, with a similar simulation scheme. We
computed the trend of clear sky radiation for each month of the year, which gave us a
mean clear sky radiation trend of $+0.14\,\%$ per year. We applied this long term
change to the clear sky irradiance, in order to create a more realistic
representation of the irradiance for the whole study period
(Figure\nobreakspace{}\ref{fig:CS-change}).

### 2024-06-09 article/article.tex
Commit 2024-06-09 21:11

The above clear sky reference values are based on the climatological AOD
and WC, hence they cannot describe accurately the long term variation of
\(\text{GHI}_\text{ref}\) due to changes in the two atmospheric
constituents, mainly AOD. As reported by \citet{Natsis2023}, there is a
long term brightening effect in the GHI data of Thessaloniki for the
period 1993 -- 2023, which for clear-sky data was attributed to
long-term changes in aerosol effects. In order to better incorporate
this change, we used, estimations of AOD change derived from two
sources. For 1993 -- 2005, \citet{Kazadzis2007} have found a change of
\(-3.8\,\%\) per year at AOD on \(340\,\text{nm}\), using a Brewer
spectrophotometer. For 2005 to 2023, we derived the trend from the
available monthly climatological data of AERONET.

@@

According to \citet{Kazadzis2007}, in the period 1997 -- 2005, the mean
AOD of \(340\,\text{nm}\) was calculated to \(0.403\) with the use of a
Brewer spectrophotometer, with a linear trend of \(-3.8±0.93\,\%\) per
year. This corresponds to a change of \(0.0153\) per year for the AOD of
\(340\,\text{nm}\) . Using the alpha Ångström coefficient of
\(\alpha = 1.6\), this translates to a change in Ångström beta
coefficient of \(\beta=0.00272\) per year (or \(\beta=0.084\) in 1997
and \(\beta=0.059\) in 2005). By interpolating the resulting clear sky
irradiance, we have a trend of \(+0.21\,\%\) per year for the clear sky
irradiance. For the period 2005 -- 2005 we used the mean monthly values
from AERONET, with a similar simulation scheme. We computed the trend of
clear sky radiation for each month of the year, which gave us a mean
clear sky radiation trend of \(+0.14\,\%\) per year. We applied this
long term change to the clear sky irradiance, in order to create a more
realistic representation of the irradiance for the whole study period
(Figure\nobreakspace{}\ref{fig:CS-change}).

>>>>

The above clear sky reference values are based on the climatological AOD
and WC, hence they cannot describe accurately the long term variation of
\(\text{GHI}_\text{ref}\) due to changes in the two atmospheric
constituents, mainly AOD. As reported by \citet{Natsis2023}, there is a
long term brightening effect in the GHI data of Thessaloniki for the
period 1993 -- 2023, which for clear-sky data was attributed to
long-term changes in aerosol effects. Therefore, an adjustment of the
\(\text{GHI}_\text{ref}\) used in this study is necessary. As AERONET
data start only in 2003, we used for the period 1993 -\/-- 2005
estimates of changes in AOD at \(340\,\text{nm}\) derived from a
collocated Brewer spectrophotometer derived from two sources. For 1993
-- 2005 \citep{Kazadzis2007} to calculate the trend in
\(\text{GHI}_\text{ref}\) during this period.

@@

According to this study, in the period 1997 -- 2005, the mean AOD at
\(340\,\text{nm}\) \(0.403\) with a trend of \(-3.8±0.93\,\%\) per year,
corresponding to a change of \(0.0153\) per year. Using an Ångström
coefficient \(\alpha = 1.6\), this translates to a change in the
Ångström coefficient \(\beta=0.00272\) per year (or \(\beta=0.084\) in
1997 and \(\beta=0.059\) in 2005).

Simulations with uvspec for the above Ångström coefficients, with WC of
\(`r round(BR[year==1997, pw_avg_mm],1)`\,\text{mm}\) and
\(15.4\,\text{mm}\) for 1997 and 2005 respectively and for a SZA of
\(55^\circ\)

By interpolating the resulting clear sky irradiance, we have a trend of
\(+0.21\,\%\) per year for the clear sky irradiance. For the period 2005
-- 2005 we used the mean monthly values from AERONET, with a similar
simulation scheme. We computed the trend of clear sky radiation for each
month of the year, which gave us a mean clear sky radiation trend of
\(+0.14\,\%\) per year. We applied this long term change to the clear
sky irradiance, in order to create a more realistic representation of
the irradiance for the whole study period
(Figure\nobreakspace{}\ref{fig:CS-change}).
